---
title: "GRTS Sampling Design for BPC 20198 Sampling
author:  Curtis C. Bohlen"
Date:  September 24, 2020
output:
  word_document: default
  pdf_document: default
  html_notebook: default
---

#Load Libraries
We are working here with spsurvey version 4.1.4, which was updated September
15th, 2020.
```{r}
library(tidyverse)
library(spsurvey)
```

# Set Random Seed
To allow repetition of sampling design.  If you run this code right before
generating a sample, the computer will generate the same sequence of random
numbers, and thus the same sample.  If you forget, you'll get another (also
perfectly valid) sample.
```{r}
set.seed(98765)
```

# Define a Simple Unstratified Design
With a ten to one oversample.

The sample is not drawn with regard to the Inspector Region. Information on the
Inspector Region will be  added later in ArcGIS after the sample and oversample
are drawn.
```{r}
SimpleDesign <- list(None=list(panel=c(PanelOne=50),
                         seltype="Equal",
                         over=500))
```

# Generate the  Spatial Sample
```{r}
SimpleSample <- grts(
         SimpleDesign,                   # as defined above
         DesignID="Pt",                  # Arbitrary string to start site codes
         SiteBegin=1001,                 # number of first sample location
         type.frame="area",              # Must be one of following: "finite",
                                         #    "linear", or "area". Depends on the
                                         #    dimensionality of the support.
         src.frame="shapefile",          # Type of source of geographic data
                                         #    defining the support. Can be
                                         #   "shapefile", "sf.object",
                                         #   "sp.object" or "att.frame"
         
         in.shape='GIS Source Files/Blubry23Final',    # path to shapefile
         
         maxlev=10,                      # maximum number of hierarchical levels to use
         
         out.shape="GIS Source Files/Blubry23RandomSD2",       # name your output shapefile
)

```
# Check The Design
```{r}
dsgnsum(SimpleSample)

```

